---
title: "Reading and writing to GeoPackage files with rgeopackage"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rgeopackage)
library(sf)
```

## Updating GeoPackage files

When using `sf` you can pass the timestamp on a per-write basis:

```{r, eval=FALSE}
nc <- st_read(system.file('shape/nc.shp', package = 'sf'), quiet = TRUE)
fixed_time <- as.POSIXct("2020-12-25 12:00:00", tz = "CET")
# or using a Date object:
# fixed_time <- as.Date("2020-12-25")
timestamp <- format(fixed_time, format = "%Y-%m-%dT%H:%M:%S.000Z", tz = "UTC")
st_write(nc, 'nc.gpkg', config_options = c(OGR_CURRENT_DATE = timestamp))
```

Note that this does not affect the value of the environment variable `OGR_CURRENT_DATE`: `config_options = c(OGR_CURRENT_DATE = timestamp)` directly sets the GDAL `OGR_CURRENT_DATE` _configuration option_ which, if unset, inherits from the `OGR_CURRENT_DATE` environment variable.
Also, note that `st_write()` ends by unsetting the configuration option, so set it in each `st_write()` statement as needed.
  
In this case please take care to format the timestamp exactly as required by the GeoPackage standard; cf. example above and [Requirement 15](https://www.geopackage.org/spec120/#r15) in version 1.2.
  
For packages relying on `rgdal` - like `sp` - it should be possible to set `OGR_CURRENT_DATE` by using `rgdal::setCPLConfigOption()` before doing the write operation.
Again, take care to format the timestamp exactly as required by the GeoPackage standard.
